---
title: "Figure4-Control/NoTreatment pH"
---
## Loading Packages
- Package files and their corresponding manuals can be found in the '02_Packages' 

```{r include=TRUE, message=FALSE, echo=TRUE}
library(readxl) #needed for loading xlsx file
library(tidyverse) #contains ggplot2, dplyr, tidyr, readr, purrr, tibble, stringr, forcats packages 
library(rstatix) #needed for tukey_hsd function
library(ggpubr) #requires tidyverse to be loaded first, needed for graphs (e.g. ggboxplot function, and ggpar
```
#Loading Data for - No Treatmant - Fig 4a - Sensor pH converted from leaf surface mV
```{r include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
SensorData<-read_excel("TableS1.xlsx",sheet = "Sensor-pH", col_types = c("numeric","numeric","text","numeric","text")) # loading excel, definning which sheet is loaded and define the type of column each is (have to set manually) - important later for stats
SensorData$Cultivar <- factor(SensorData$Cultivar, levels = c("Beryl","G122","Eldorado", "ICA Bunsi", "Montrose", "Othello", "WM-1","WM-12")) #order the Cultivars (for graph later on))
```

## Splitting Data by Block - Blocks 1-3: Control/No Treatment, Block 4: Wounding Treatment
```{r include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
SensorData<- SensorData %>% filter(Block < 4) #removes Block 4 from SensorData (Wounded Treatment)- will be used for inoculated plots in Fig6a
```

## Stats- Two-way ANOVA - Cultivar and Block for Figurea4a. Data showed in Table S2.
```{r echo=FALSE}
summary(aov(pH ~ Cultivar + Block + Cultivar*Block, data = SensorData))
```

#Figure4a - Control/No Treatment - Sensor pH
```{r message=FALSE, warning=FALSE}
Fig4a<-ggboxplot(SensorData,"Cultivar", "pH", add="jitter",color="TimePoint", title="Sensor - Leaf Surface mV Converted to pH")+
theme(plot.title = element_text(hjust = 0.5, vjust = 2)) + #Move title to middle, move up a bit
theme(plot.title = element_text(color="black", size=12)) + # change title font size
xlab("") #remove the x axis label (Cultivar)

Fig4a <- Fig4a + theme(axis.text.x = element_text(size=12,angle = 90,vjust = 0.4, hjust=1,color="black"))# x axis font size
Fig4a <- Fig4a + theme(axis.text.y = element_text(size=12)) # y axis font size
Fig4a <- Fig4a + theme(axis.title.x = element_text(size=12)) #changing x axis label font size
Fig4a <- Fig4a + theme(axis.title.y = element_text(size=12)) #changing y axis label size
Fig4a<-ggpar(Fig4a, legend = "none") # removes Legend
Fig4a
```

## Loading data from No Treatment - Manually extracted pH - For Fig 4b
```{r echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
ManualData<-read_excel("TableS1.xlsx",sheet = "Manual-pH", col_types = c("numeric","numeric","text","numeric","text")) # loading excel, definning which sheet is loaded and define the type of column each is (have to set manually) - important later for stats
ManualData$Cultivar <- factor(ManualData$Cultivar, levels = c("Beryl","G122","Eldorado", "ICA Bunsi", "Montrose", "Othello", "WM-1","WM-12")) #order the Cultivars (for graph later on))
```

## Splitting Data by Block - Blocks 1-3: No Treatment, Block 4: Wounding Treatment
```{r include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
ManualData<- ManualData %>% filter(Block < 4) #removes Block 4 from ManualData (Wounded Treatment)- will be used for inoculated plots in Fig6a
```

## Stats- Two-way ANOVA - Cultivar and Block for Fig4b. Data showed in Table S3.
```{r echo=FALSE}
summary(aov(pH ~ Cultivar + Block + Cultivar*Block, data = ManualData))
```

## Generating Figure4b
```{r echo=FALSE}
Fig4b<-ggboxplot(ManualData,"Cultivar", "pH", add="jitter",color="TimePoint", title="Manual - Leaf Apoplastic Fluid") +
theme(plot.title = element_text(hjust = 0.5, vjust = 2)) + #Move title to middle, move up a bit
theme(plot.title = element_text(color="black", size=12)) + # change title font size
ylim(3.9, 8.1) + #ensures the y axis are the same between 4a and 4b
xlab("") #remove the x axis label (Cultivar)

Fig4b <- Fig4b + theme(axis.text.x = element_text(size=12,angle = 90,vjust = 0.4, hjust=1,color="black"))# x axis font size
Fig4b <- Fig4b + theme(axis.text.y = element_text(size=12)) # y axis font size
Fig4b <- Fig4b + theme(axis.title.x = element_text(size=12)) #changing x axis label font size
Fig4b <- Fig4b + theme(axis.title.y = element_text(size=12)) #changing y axis label size
Fig4b<-ggpar(Fig4b, legend = "none") # removes Legend
Fig4b
```

#Combining Fig4a and Fig4b to make Fig4
```{r}
Fig4 <- ggarrange(Fig4a, Fig4b, ncol = 2, nrow = 1, labels = "auto", legend = "none", widths = c(2,1.4)) #width squashes Panel A graph
Fig4
```

#Saving Figure4
```{r}
#Saving the plot as a tiff and pdf
ggsave(plot=Fig4, file="Fig4-Control-pH.tiff", units="cm", width=18, height=12, dpi=600, compression='lzw')
ggsave(plot=Fig4, file="Fig4-Control-pH.pdf", units="cm", width=18, height=12, dpi=600)
```

#Table S4 - Comparing pH changes in both approaches
## Loading data from No Treatment - Manually extracted pH - For Fig 4b
```{r echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
CompareData<-read_excel("TableS1.xlsx",sheet = "Compare Approaches", col_types = c("numeric","numeric","text","numeric","text")) # loading excel, definning which sheet is loaded and define the type of column each is (have to set manually) - important later for stats
CompareData <- na.omit(CompareData) #removes NAs (some WM-12 rows)
#CompareData$Cultivar <- factor(ManualData$Cultivar, levels = c("Beryl","G122","Eldorado", "ICA Bunsi", "Montrose", "Othello", "WM-1","WM-12")) #order the Cultivars (for graph later on))
```

## Stats- Two-way ANOVA - Cultivar and Measurement_Type for Table S4.
```{r echo=FALSE}
summary(aov(pH ~ Cultivar + Measurement_Type+ Cultivar*Measurement_Type, data = CompareData))
```

## Post-hoc Tests for calculating individual p values when comparing pre and post treatment within each Cultivar
```{r echo=FALSE}
CompareDataposthoc<-CompareData %>% group_by(Cultivar) %>% tukey_hsd(pH ~ Measurement_Type) 
CompareDataposthoc
```
