---
title: "Figure5-Wounding-pHManualvsSensor"
---
## Loading Packages
- Package files and their corresponding manuals can be found in the '02_Packages' 

```{r include=TRUE, message=FALSE, echo=TRUE}
library(readxl) #needed for loading xlsx file
library(tidyverse) #contains ggplot2, dplyr, tidyr, readr, purrr, tibble, stringr, forcats packages 
library(rstatix) #needed for tukey_hsd function
library(ggpubr) #requires tidyverse to be loaded first, needed for graphs (e.g. ggboxplot function, and ggpar
```


# Figure5a - Sensor pH converted from leaf surface mV
```{r include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
SensorData<-read_excel("TableS1.xlsx",sheet = "Sensor-pH", col_types = c("numeric","numeric","text","numeric","text")) # loading excel, definning which sheet is loaded and define the type of column each is (have to set manually) - important later for stats
SensorData$Cultivar <- factor(SensorData$Cultivar, levels = c("Beryl","G122","Eldorado", "ICA Bunsi", "Montrose", "Othello", "WM-1","WM-12")) #order the Cultivars (for graph later on))
```

## Splitting Data by Block - Blocks 1-3: No Treatment, Block 4: Wounding Treatment
```{r include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
SensorData<- SensorData %>% filter(Block == 4) #removes Blocks 1-3 (No Treatment), keeps Block 4 from SensorData (Wounded Treatment)- will be used for Fig 5
```

## Stats- Two-way ANOVA - Cultivar and TimePoint (i.e. Pre-and post treatment) for Figure5b. Data showed in Table S5.
```{r echo=FALSE}
summary(aov(pH ~ Cultivar + TimePoint + Cultivar*TimePoint, data = SensorData))
```

## Post-hoc Tests for calculating individual p values when comparing pre and post treatment within each Cultivar - then manually add p values to Figure5a in ppt.
```{r echo=FALSE}
Fig5aposthoc<-SensorData %>% group_by(Cultivar) %>% tukey_hsd(pH ~ TimePoint)
Fig5aposthoc
```

#Figure5a - Sensor pH Wounded
```{r message=FALSE, warning=FALSE}
SensorData$TimePoint <- factor(SensorData$TimePoint, levels = c("Pre-wounding", "Post-wounding")) #ensure that pre and then post treatment appears in that order on plot 2
Fig5a<-ggboxplot(SensorData,"Cultivar", "pH", add="jitter",color="TimePoint", title="Sensor - Leaf Surface mV Converted to pH")+
theme(plot.title = element_text(hjust = 0.5, vjust = 2)) + #Move title to middle, move up a bit
theme(plot.title = element_text(color="black", size=12)) + # change title font size
xlab("") #remove the x axis label (Cultivar)

Fig5a <- Fig5a + theme(axis.text.x = element_text(size=12,angle = 90,vjust = 0.4, hjust=1,color="black"))# x axis font size
Fig5a <- Fig5a + theme(axis.text.y = element_text(size=12)) # y axis font size
Fig5a <- Fig5a + theme(axis.title.x = element_text(size=12)) #changing x axis label font size
Fig5a <- Fig5a + theme(axis.title.y = element_text(size=12)) #changing y axis label size
Fig5a<-ggpar(Fig5a, legend = "bottom") # Legend at bottom
Fig5a<-ggpar(Fig5a, legend.title = "") # Remove legend title which was 'TimePoint'
Fig5a
```



## Loading data from Manually extracted pH - For Fig 5b
```{r include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
ManualData<-read_excel("TableS1.xlsx",sheet = "Manual-pH", col_types = c("numeric","numeric","text","numeric","text"))  # loading excel, definning which sheet is loaded and define the type of column each is (have to set manually) - important later for stats
ManualData$Cultivar <- factor(ManualData$Cultivar, levels = c("Beryl","G122","Eldorado", "ICA Bunsi", "Montrose", "Othello", "WM-1","WM-12")) #order the Cultivars (for graph later on)
ManualData <- na.omit(ManualData) #removes all rows with NA
ManualData$TimePoint <- factor(ManualData$TimePoint, levels = c("Pre-wounding", "Post-wounding")) #order the treatments pre and post treatment (for graph later on)
```

## Splitting Data by Block - Blocks 1-3: No Treatment, Block 4: Wounding Treatment
```{r include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
ManualData<- ManualData %>% filter(Block == 4) #removes Blocks 1-3 (No Treatment), keeps Block 4 from ManualData (Wounded Treatment)- will be used for Fig 5b
```

## Generating Figure5b
```{r echo=FALSE}
Fig5b<-ggplot(ManualData,aes(x=Cultivar,y=pH, fill=TimePoint)) + # Fill=TimePoint means the colour is based on the TimePoint column i.e. post or pre treatment 
geom_point(aes(color = TimePoint), size = 3, position = position_dodge(width=0.3)) + #adds data points to plot
xlab("Cultivar") + #Set x axis label
theme_bw() + #Set theme of graph
theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ #remove previous grid lines that are added with theme_bw 
theme(panel.border = element_blank(), panel.grid.major = element_blank(), axis.line = element_line(colour = "black")) + #remove previous grid lines that are added with theme_bw
theme(axis.text.x = element_text(size=12,angle = 90,vjust = 0.4, hjust=1, color="black")) + # x axis font size
theme(axis.text.y = element_text(size=12, color="black")) + # y axis font size
theme(plot.title = element_text(color="black", size=12)) + # change title font size
xlab("") #remove the x axis label (Cultivar)

Fig5b <- Fig5b + ggtitle("Manual - Leaf Apoplastic Fluid") + #Defining title
theme(plot.title = element_text(hjust = 0.5, vjust=2)) #Centering title
Fig5b <- Fig5b + theme(axis.title.x = element_text(size=12)) #changing x axis label font size
Fig5b <- Fig5b + theme(axis.title.y = element_text(size=12)) #changing y axis label size
Fig5b<-ggpar(Fig5b, legend.title = "") # Remove legend title which was 'TimePoint'
Fig5b<-ggpar(Fig5b, legend = "bottom") # Legend at bottom
Fig5b
```


#Combining Fig5a and Fig5b to make Fig5
```{r}
Fig5 <- ggarrange(Fig5a, Fig5b, ncol = 2, nrow = 1, labels = "auto", legend = "bottom", widths = c(2,1.4)) #width squashes Panel A graph
Fig5 <- annotate_figure(Fig5, top = text_grob("Wounding Treatment", color = "black", face = "bold", size = 12)) #Adding a main title above the panels
Fig5
```

#Saving Figure5
```{r}
#Saving the plot as a tiff and pdf
ggsave(plot=Fig5, file="Fig5-Wounded-pH.tiff", units="cm", width=18, height=12, dpi=600, compression='lzw')
ggsave(plot=Fig5, file="Fig5-Wounded-pH.pdf", units="cm", width=18, height=12, dpi=600)
```




#Analysis of difference in change in pH detected using the Manual pH or Sensor pH Approach
## Loading pH Change data
```{r include=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
CombinedData<-read_excel("TableS1.xlsx",sheet = "Combined-pH-change", col_types = c("text","numeric","numeric","text")) # loading excel, definning which sheet is 
```

#Wound Treated
## Stats- Two-way ANOVA of the Change in pH (Post-Pre) 'pH_change' vs 'Cultivar' vs 'TimePoint'(Pre or Post) vs 'Measurement_Type' i.e. either 'Manual' Leaf apoplastic fluid or 'Sensor' leaf surface mV converted to pH 'Measurement_Type'. Presented in Table S6.
```{r echo=FALSE}
summary(aov(pH_change ~ Cultivar + Measurement_Type +Cultivar/Measurement_Type, data = CombinedData)) 
```

## Post-hoc Tests for calculating individual p values when comparing pre and post treatment within each Cultivar. Presented in Table S7.
```{r echo=FALSE}
WoundpHchangeposthoc<-CombinedData %>% group_by(Cultivar) %>% tukey_hsd(pH_change ~ Measurement_Type) 
WoundpHchangeposthoc
```