---
title: "1. BaselineSimulation"
author: "Henry Cordoba"
output: html_document
---

### Simulation of genetic gain when parents are selected and --ONCE-- Parameters have been set

Create a matrix where we will store the results of Genetic Gain and genetic values
```{r}
Results <- matrix(nrow = 2, ncol = 6)
rownames(Results) <- c("GeneticGain", "DeltaVariance")
colnames(Results) <- c("High_High", "SE_HxH", "Low_Low","SE_LxL", "High_Low","SE_HxL")

PipelineData <- matrix(nrow = 7, ncol = 2)
rownames(PipelineData) <- c("F1","F2","F3","F4","PYT","AYT", "Variety")
colnames(PipelineData) <- c("PopSize", "GVs")

```

1. Define populations and replace phenotypes

```{r}
load("founderPop.RData")
parents0 = newPop(founderPop, simParam = SP)
parents0@pheno <- phenotype

save(parents0, file="parents0.SY.RData")

load("parents0.SY.RData")

```

# crossing schemes

2. Define crossing scheme 1

``` {r}
# before doing the crosses, define the crossing plan: A matrix with 2 column (Female x Male) -- change according to the id number.

#parents@iid
crossPlanHH <- matrix(nrow = 20, ncol = 2)
colnames(crossPlanHH) <- c("Parent1", "Parent2")

#High x High Mutations parents

crossPlanHH[,1] <- c(5,217,5,266,5,181,229,181,326,217,266,217,229,326,266)
crossPlanHH[,2] <- c(181,5,229,5,326,217,181,266,181,229,217,326,266,229,326)

### BASED ON GENETIC LOAD

crossPlanHH[,1] <- c(1,2,3,4,9,10,11,18,22,26,27,28,29,30,33,36,37,38,39,40)
crossPlanHH[,2] <- c(10,38,26,40,3,33,37,39,28,30,29,18,2,4,11,22,36,9,1,27)



```

3. when changing the crossing plan - 2

```{r}
crossPlanLL <- matrix(nrow = 20, ncol = 2)
colnames(crossPlanLL) <- c("Parent1", "Parent2")

# Low x Low mutations parents

crossPlanLL[,1] <- c(78,101,78,142,78,99,133,99,99,101,142,101,142,133,286)
crossPlanLL[,2] <- c(99,78,133,78,286,101,99,142,286,133,101,286,133,286,142)


### BASED ON GENETIC LOAD

crossPlanLL[,1] <- c(5,6,7,8,12,13,14,15,16,17,19,20,21,23,24,25,31,32,34,35)
crossPlanLL[,2] <- c(31,21,15,13,19,20,32,12,8,5,6,17,35,25,14,24,16,23,7,34)

```

Crossing plan - 3

```{r}
crossPlanHL <- matrix(nrow = 20, ncol = 2)
colnames(crossPlanHL) <- c("Parent1", "Parent2")

# High x Low mutations parents

crossPlanHL[,1] <- c(55,63,78,92,99,101,5,181,217,229,326,266)
crossPlanHL[,2] <- c(5,181,217,229,326,266,133,142,209,210,286,170)

### BASED ON GENETIC LOAD

crossPlanHL[,1] <- c(31,21,15,13,19,20,32,12,8,5,6,17,35,25,14,24,16,23,7,34)
crossPlanHL[,2] <- c(1,2,3,4,9,10,11,18,22,26,27,28,29,30,33,36,37,38,39,40)

```

```{r}
# Save crossingSchemes
save(crossPlanHH, crossPlanHL, crossPlanLL, file = "CrossingPlans.RData")
```


##### Stop here, you created all the files. Go to next script to run all in loops ## 

